%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%            请在此填写摘要            %%
%% 请勿编译/排版此文件,请编译PAPER.tex!  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}\small
    Here is the abstract of your paper.

    Firstly, that is ...

    Secondly, that is ...
We analyze the correlation between drug identification counts socio-economic factors by Apriori, which is an algorithm for frequent item set mining and association rule learning over transactional databases. From the result, we draw a conclusion that adults with some college education and with no education beyond high school who don't get married, men with no wife present and women with no husband and own children present are likely to use/abuse opioids, and the growth of its percentage contributes to the growth of the percentage of opioid use and addiction. 
    Finally, that is ...

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号'%'去除，以使其生效；
    % 若您不使用，可直接将这段注释删除
    \vspace{5pt}
    \textbf{Keywords}: MATLAB, mathematics, LaTeX.

Governor Jay Inslee 

Office of the Governor 

PO Box 40002

Olympia, WA 98504-0002 

Dear Governor Inslee:

I write to you on behalf of the MCM team 1902639. We are extremely concerned about the opioid crisis in the United States. Investigation shows that opioid use and addiction have spread among a large number of states and counties. We hope to help you improve the traffic conditions.

Opioid use and addiction could bring about health and major economy problems. Firstly, opioids lead to a large number of negative health, such as opioid use disorder, hepatitis, and HIV infections, and neonatal abstinence syndrome. Secondly, opioids overdoes can lead to death. Thirdly, it will be difficult to fill positions of high-tech and reliable workers if the crisis spreads to special population such as the high-educated. Lastly, if the percentage of people with opioid addiction increases within the elderly, it will affect the health care costs and assisted living facility staffing.

After an in-depth study of the drug conditions in 5 states (Ohio, Pennsylvania, Virginia, West Virginia and Kentucky), we have come up with some ideas that can help address this issue.

Sincerely yours

MCM 2019 Team 1902639
\end{abstract}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 如不理解以下部分中各命令的含义，请勿修改！ %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%---------以下生成sheet页----------
% 下面的语句可调整全文行距为标准值的0.6倍，请自行使用
% \renewcommand{\baselinestretch}{0.6}\normalsize
\maketitle  			% 生成sheet页
\thispagestyle{empty}   % 不要页眉页脚和页码
\setcounter{page}{-100} % 此命令仅是为了避免页码重复报错，不要在意

%---------以下生成目录----------
\newpage
\tableofcontents
\thispagestyle{empty}   % 不要页眉页脚和页码
\newpage

%---------以下生成正文----------
\setlength\parskip{0.8\baselineskip}  % 调整段间距
\setcounter{page}{1}    % 从正文开始计页码
\pagestyle{fancy}